Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}. \textcolor{red}{Power peak, power surge and energy consumption were estimated based on visiting and survey applied in each house (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.

@@

\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the coded problem (software created by authors) to be solved. Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.}

@@

\textcolor{red}{
\textit{Simulation Tool:} Only HOMER Pro was used. The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification can change the comparative.}

\textcolor{red}{
\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from data bases available online. However, considering that riverside communities do not have weather stations, the data used at this work come from the closest municipality (Manaus in all case studies), where stations collect regularly those data. Therefore, the most accurate should be the use of weather stations in each location to obtain the data.}

>>>>

We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}. \textcolor{red}{Power peak, power surge, and energy consumption were estimated based on visiting and survey applied to each house (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.

@@

\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the implemented model (software created by authors) to be solved. Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.}

@@

\textcolor{red}{
\textit{Simulation Tool:} Only HOMER Pro was used. The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparative.}

\textcolor{red}{
\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online \textcolor{green}{cite them here?}. However, considering that riverside communities do not have weather stations, the data used in our study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data. Therefore, the most accurate should be the use of weather stations in each location to obtain the data.}
